Flexibility of interactions depends on habitat suitability

### 2019-08-29 paper/manuscript.Rmd
Random effects results

readd(fig_sensitivity_analysis)
```
loadd(bayesian_r2_baseline)
loadd(parameter_posterior_summary)

random_cor <- parameter_posterior_summary %>% 
  as.data.frame() %>%
  tibble::rownames_to_column(var = "parameter") %>%
  dplyr::filter(parameter == "cor_org_id__Intercept__scaled_suitability")
```

@@

@@

>>>>

readd(fig_sensitivity_analysis)
```

```{r model-results-calculations}
loadd(bayesian_r2_baseline)
loadd(parameter_posterior_summary)

random_cor <- parameter_posterior_summary %>%
  dplyr::filter(parameter == "cor_org_id__Intercept__scaled_suitability")

sd_loc_id <- parameter_posterior_summary %>% 
  dplyr::filter(stringr::str_detect(parameter, "sd_loc_id__Intercept"))

sd_org_id <- parameter_posterior_summary %>% 
  dplyr::filter(stringr::str_detect(parameter, "sd_org_id__Intercept"))

sd_org_id_suitability <- parameter_posterior_summary %>% 
  dplyr::filter(stringr::str_detect(parameter, "sd_org_id__scaled_suitability"))
```

@@

The group level variation among communities was larger than that among species.
The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets). 
Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].

@@

# Discussion
